What We Eval in the Shadows

### 2021-04-02 paper/main.tex
stuff

The environment in which evaluation happens determines what will be visible to
the computation started by \eval, and the potential reach of side-effects. The
second argument to \eval, \c{envir}, defines the evaluation environment of the
expression. That argument can be omitted, in which case the default value is
\c{parent.frame()} which returns the caller of the \eval function.

Other possible values for the environment include, lists, dataframes, pairlists,
integers and \c{Null}. Lists and dataframe are coerced to new environments,
integers values are passed to the \c{sys.call} function which returns the
environment of a stack frame at the requested offset.

>>>>

The environment in which evaluation happens determines what is visible to the
computation started by \eval, and the potential reach of its side-effects. The
second argument to \eval, \c{envir}, defines that environment. It can be
omitted, in which case its defaults to \c{parent.frame()} which returns the
caller's environment. Other possible values for \c{envir} include, lists,
dataframes, pairlists, integers and \c{Null}. Lists and dataframe are coerced to
new environments, integer values are passed to \c{sys.call} which returns the
environment of a stack frame at the requested offset.
